\documentclass{resume}
\usepackage[left=0.4in,top=0.4in,right=0.4in,bottom=0.4in]{geometry}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{YashPal Singh}
\address{+91 8439345464 \\ Mathura, Uttar Pradesh, India}
\address{\href{mailto:yashpal9rx@gmail.com}{yashpal9rx@gmail.com} \\ \href{https://www.linkedin.com/in/yshplsngh}{Linkedin} \\ \href{https://github.com/yshplsngh}{Github} \\ \href{https://yshplsngh.in}{Portfolio}}

\begin{document}
\begin{rSection}{TECHNICAL SKILLS}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Languages & JavaScript, Java \\
Frontend  & ReactJS, Next.js, Redux, TypeScript, Framer-motion \\
Backend & Node.js, Express, MongoDB, SQL (Postgres), Prisma, TanStack Query \\
Concepts & REST APIs, Redis \\
Developer Tools & Git, Docker, Linux, IntelliJ. \\
\end{tabular}
\end{rSection}


\begin{rSection}{EXPERIENCE}
\textbf{Database Management Trainee} \hfill Jun 2023 – Jul 2023\\
Job-Oriented Value-Added Course, GLA University, Mathura
 \begin{itemize}
    \itemsep -5pt {}
     \item Learn advanced MongoDB querying techniques and CRUD operations.
     \item Designed and optimized databases for multiple course projects.
     \item Implemented database management principles in real-world scenarios.
 \end{itemize}
\end{rSection} 




\begin{rSection}{PROJECTS}

\textbf{Feedback Testimonial} \hfill 
\href{https://testimonial.yshplsngh.in}{Live} |
\href{https://github.com/yshplsngh/Feedback-Testimonial}{GitHub}
\begin{itemize}
  \itemsep -5pt {}
  \item \textbf{Tech stack}: ReactJS, Redux, TypeScript, Node.js, PostgreSQL, Prisma, Redis, Docker.
  \item Developed a platform to collect, manage, and display customer testimonials and reviews.
  \item Allows easily gather feedback from their clients and display them on their websites.
  \item Optimized the feedback process, enabling faster integration and reducing manual effort by 35%
  % \item Implemented secure auth with sessions, cutting login times by 40\% and bolstering security.
  \item Automated backend deployment via Docker images, GitHub Actions, Docker Hub, and EC2 SSH.

\end{itemize}

\textbf{Shop Mart} \hfill \href{https://github.com/yshplsngh/shop-mart}{GitHub}
\begin{itemize}
  \itemsep -5pt {}
    \item \textbf{Tech stack}: ReactJS, Typescript, Node.js, MongoDB, and Docker.
    \item Designed a scalable e-Commerce platform for seamless online shopping experiences.
    \item Established a robust role-based access control system for both customers and admins.
    \item Integrated GoAPI, Biteship, and Xendit APIs for enhanced functionality.

\end{itemize}

\textbf{Note-Taking} \hfill \href{https://github.com/yshplsngh/Blog-Site}{GitHub}
 \begin{itemize}
    \itemsep -6pt {}
      \item \textbf{Tech stack}: ReactJS, Redux, TypeScript, Express.js, MongoDB, JWT
      \item A platform allow users to effortlessly create, modify, and organize their notes.
      \item Integrated Access token and Refresh token rotation for secure user access.
      % \item Optimized performance using Redux caching for client-side data access.
      \item Enhanced data retrieval speed by 35\% using RTK-Query, improving load times.

     
 \end{itemize}

% \textbf{Screen Recorder} \hfill \href{https://github.com/yshplsngh/ScreenRecorder}{Github}
% \begin{itemize}
%   \itemsep -6pt {}
%   \item Built a browser-based screen recording app using React and TypeScript.
%   \item Utilized MediaStream API for video and audio capture.
%   \item Implemented local download and sharing features.
% \end{itemize}

\end{rSection}

\begin{rSection}{ADDITIONAL INFORMATION}
\begin{itemize}
  \itemsep -5pt {}
  \item Deployed Multiple Backend in docker container on AWS using CI/CD pipeline.
  \item Automate Project Deployment using GitHub actions.
  % \item Solved over 100+ coding problem on LeetCode, demonstrating strong problem-solving skills
\end{itemize}
\end{rSection}

\begin{rSection}{EDUCATION}
{\bf Bachelor of Technology in Computer Science} \hfill {Expected June 2025}\\
GLA University, Mathura, India.

{\bf Higher Secondary Education} \hfill {June 2017–May 2021}\\
Saraswati vidya mandir.
\end{rSection}

\end{document}